JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-02 report/paper.tex
Report: Added images and wrote about crawling Anime Lyrics.

\easyfigdefault{placement={!htb}, max width=20pc, max height=\textheight, keepaspectratio}

@@

Secondly, finding information on the song itself can assist the listener in learning foreign languages. Repetition is the best methods for learning. Listening to enjoyable music and recognizing new words each time the song is played is a fun way to strengthen one's language capabilities through repetition. Many music players such as foobar2000 and Rocket Player will display the lyrics of a song that is being played so long as those lyrics have been embedded into the music file as a tag. An example screenshot of Rocket Player showing a song's lyrics is in Figure~\ref{fig:res/rocket-player.png} This feature can be used in tandem with the learner's interest in following along with the song to promote learning the language. If one is clever, they could put the same lyrics into the karaoke variant of the song and practice singing to improve their reading and speaking abilities. Regardless of the reason, they user would need to find the full lyrics from the song. We want to help with this cause.

\Figure[caption="Rocket Player Displaying Song Lyrics]{res/rocket-player.png}

Finally, if someone finds a song they like, there is a good chance that the songs made by that song's producer would also be likable.

@@

@@

\Figure[caption="cmd.exe on Windows Failure"]{res/cmd_search_fail.png}

@@

\Figure[caption="PuTTY on Windows Success"]{res/putty_search_success.png}

>>>>

\easyfigdefault{placement={!htb}, max width=20pc, max height=.5\textheight, keepaspectratio}

@@

Secondly, finding information on the song itself can assist the listener in learning foreign languages. Repetition is the best methods for learning. Listening to enjoyable music and recognizing new words each time the song is played is a fun way to strengthen one's language capabilities through repetition. Many music players such as foobar2000 and Rocket Player will display the lyrics of a song that is being played so long as those lyrics have been embedded into the music file as a tag. An example screenshot of Rocket Player showing a song's lyrics is in Figure~\ref{fig:res/rocket-player.png}. This feature can be used in tandem with the learner's interest in following along with the song to promote learning the language. If one is clever, they could put the same lyrics into the karaoke variant of the song and practice singing to improve their reading and speaking abilities. Regardless of the reason, they user would need to find the full lyrics from the song. We want to help with this cause.

\Figure[caption={Rocket Player Displaying Song Lyrics}, max height=.3\textheight]{res/rocket-player.png}

Finally, if someone finds a song they like, there is a good chance that the song's producer has made other likable songs. Our search engine would be one more avenue for users to find new material to enjoy themselves with.

@@

Before we could make a search engine, we would need to have material to search through. The Internet already has a great amount of data on it, but we need to extract that information. In order to do that, we used programming languages that were able to retrieve web pages so that we could save those pages on our hard drives. Later, we would program some way to parse those pages and get the data we wanted. The final product would be a standardized format for documents (a.k.a. docs) that the indexer would interpret.

\subsection{Anime Lyrics dot Com}

Anime Lyrics dot Com is a multi-layered site, so it took a considerable amount of time determining how to best crawl it. The home page lists all of the genres of music stored on Anime Lyrics dot Com. Despite what their name may imply, they also store lyrics for dance, dance CD, doujin, video game, and J-Pop music. Each genre has an index.htm file listing all of the albums belonging to that category. Each album name points to an index.htm in a deeper directory. The album page at this area lists all of the songs in that album. The songs are in the same directory as the album, but they do not have the name index.htm, so they stand out in the address bar. The name index.htm is a default name that the web browser will try to access, so the URL usually omits this. By consequence, we only see a ".htm" URL when looking at a song.

Graphically, the general structure of Anime Lyrics dot Com can be seen in Figure~\ref{fig:res/animelyrics_format.png}. All folders shown have an index.htm in them, but the album folders all hold song web pages as well.

\Figure[caption={Anime Lyrics dot Com Structure}, max width=5pc]{res/animelyrics_format.png}

When the pages are parsed to generate the indexable docs, the folder structure is retained, but there will be no more index.htm pages left over.

All Anime Lyrics dot Com crawling and parsing was done in Python 2 using the Beautiful Soup (2) library and a few regular expressions. All crawling was done with a one-to-two second randomized delay so as to not hammer their server. Two scripts were ran at once simultaneously on the same computer to get more songs at once during the final phase of the crawling.

The genre pages were grabbed by hand and the full list of albums were retrieved from that. The album pages were stored locally, but it was quickly discovered that even the plain text produced by Anime Lyrics dot Com created an extremely large amount of data that was stored. About 60 MB of album pages were downloaded. Most of this was boiler plate code such as the navigation bar, embedded scripts, and formatting to make the web page display nicely.

Before beginning the crawling of the song pages, a method of getting rid of the unnecessary data was worked on. Without making too many assumptions about the format of the nearly 40,000 song pages Anime Lyrics dot Com had available, it was decided that the chunk of code above and below the song lists of each album page would be cropped out before being saved to the hard drive. As an extra precaution, Beautiful Soup was used to re-create valid HTML before saving the crawled album page. This was to ensure that later parsing of the song page would hopefully be consistent.

During the development process, a total of three different systems had seen work with the codebase being worked on. Python 2 with Beautiful Soup 2 had ran the script on Windows 7, Windows 8, and Xubuntu (Linux). In doing so, non-cross-platform bugs surfaced in the code. Of particular interest was that the crawler would outright crash on Windows. The problem was that Beautiful Soup was capable of using a slew of different HTML parsers and it would select a default for you. The default was usually a bad one that shipped with Python, so on the Windows operating systems, the lxml library was installed as well. With all three systems using lxml for parsing the web pages, the code became consistent in behavior and cross-platform

12,654 songs were scoured.

@@

\Figure[caption=Search Failure With cmd.exe]{res/cmd_search_fail.png}

@@

\Figure[caption=Search Success With PuTTY]{res/putty_search_success.png}
